---
title: "Calculate replications"
author: sheli and nadav
date: June 4, 2018
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# initial t-tests

```{r}

filePathDefects <- choose.files()
Defects_in_argaz <- read.csv(filePathDefects,header=TRUE)

filePathUtility <- choose.files()
daily_utility <- read.csv(filePathUtility,header=TRUE)

filePathProfit <- choose.files()
daily_profit <- read.csv(filePathProfit,header=TRUE)

```



# average defects in argaz per replication

### existing situation
```{r}
test1 <-  t.test(x= Defects_in_argaz$existing.situation ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test1)
ci1 <-  c(test1$conf.int[1],test1$conf.int[2])
print(ci1)
meanFlow1 <- test1$estimate
delta1 <- test1$conf.int[2]-meanFlow1
print(delta1)
precise1 <-  delta1/meanFlow1
paste0("the relative accuracy for average defects in argaz per replication for existing situation is: ",  precise1)
```

### alternative1
```{r}
test2 <-  t.test(x= Defects_in_argaz$alternative1 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test2)
ci2 <-  c(test2$conf.int[1],test2$conf.int[2])
print(ci2)
meanFlow2 <- test2$estimate
delta2 <- test2$conf.int[2]-meanFlow2
print(delta2)
precise2 <-  delta2/meanFlow2
paste0("the relative accuracy for average defects in argaz per replication for alternative1 is: ",  precise2)

```
### alternative2
```{r}
test3 <-  t.test(x= Defects_in_argaz$alternative2 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test3)
ci3 <-  c(test3$conf.int[1],test3$conf.int[2])
print(ci3)
meanFlow3 <- test3$estimate
delta3 <- test3$conf.int[2]-meanFlow3
print(delta3)
precise3 <-  delta3/meanFlow3
paste0("the relative accuracy for average defects in argaz per replication for alternative2 is: ",  precise3)

```

# average daily workers utility

### existing situation
```{r}
test4 <-  t.test(x= daily_utility$existing.situation ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test4)
ci4 <-  c(test4$conf.int[1],test4$conf.int[2])
print(ci4)
meanFlow4 <- test4$estimate
delta4 <- test4$conf.int[2]-meanFlow4
print(delta4)
precise4 <-  delta4/meanFlow4
paste0("the relative accuracy for average daily workers utility for existing situation is: ",  precise4)
```
##חורג מהדיוק היחסי - 0.074
### alternative1
```{r}
test5 <-  t.test(x= daily_utility$alternative1 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test5)
ci5 <-  c(test5$conf.int[1],test5$conf.int[2])
print(ci5)
meanFlow5 <- test5$estimate
delta5 <- test5$conf.int[2]-meanFlow5
print(delta5)
precise5 <-  delta5/meanFlow5
paste0("the relative accuracy for average daily workers utility for alternative1 is: ",  precise5)
```
# חורג מהדיוק היחסי - 0.074
### alternative2
```{r}
test6 <-  t.test(x= daily_utility$alternative2 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test6)
ci6 <-  c(test6$conf.int[1],test6$conf.int[2])
print(ci6)
meanFlow6 <- test6$estimate
delta6 <- test6$conf.int[2]-meanFlow6
print(delta6)
precise6 <-  delta6/meanFlow6
paste0("the relative accuracy for average daily workers utility for alternative2 is: ",  precise6)
```
##חורג מהדיוק היחסי - 0.074
# avarage daily profit

### existing situation
```{r}
test7 <-  t.test(x= daily_profit$existing.situation ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test7)
ci7 <-  c(test7$conf.int[1],test7$conf.int[2])
print(ci7)
meanFlow7 <- test7$estimate
delta7 <- test7$conf.int[2]-meanFlow7
print(delta7)
precise7 <-  abs(delta7/meanFlow7)
paste0("the relative accuracy for avarage daily profit for existing situation is: ",  precise7)
```
### alternative1
```{r}
test8 <-  t.test(x= daily_profit$alternative1 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test8)
ci8 <-  c(test8$conf.int[1],test8$conf.int[2])
print(ci8)
meanFlow8 <- test8$estimate
delta8 <- test8$conf.int[2]-meanFlow8
print(delta8)
precise8 <-  abs(delta8/meanFlow8)
paste0("the relative accuracy for avarage daily profit for alternative1 is: ",  precise8)
```
##חורג מהדיוק היחסי - 0.074
### alternative2
```{r}
test9 <-  t.test(x= daily_profit$alternative2 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test9)
ci9 <-  c(test9$conf.int[1],test9$conf.int[2])
print(ci9)
meanFlow9 <- test9$estimate
delta9 <- test9$conf.int[2]-meanFlow9
print(delta9)
precise9 <-  abs(delta9/meanFlow9)
paste0("the relative accuracy for avarage daily profit for alternative2 is: ",  precise9)
```
##חורג מהדיוק היחסי - 0.074
#קירוב גס calculation requiered numbe of replication.first time
```{r}
z <- (meanFlow4*0.074)
print(z)
kamut_rizot_existing_situation <- 30*(delta4/z)^2
paste0("the number of required replication for existing situation is:", kamut_rizot_existing_situation)

x <- (meanFlow8*0.074)
print(x)
kamut_rizot_alternative1_a <- 30*(delta8/x)^2
paste0("the number of required replication for alternative1 is:", kamut_rizot_alternative1_a)

v <- (meanFlow6*0.074)
print(v)
kamut_rizot_alternative1_b <- 30*(delta6/v)^2
paste0("the number of required replication for alternative1 is:", kamut_rizot_alternative1_b)


y <- (meanFlow9*0.074)
print(y)
kamut_rizot_alternative2_b <- 30*(delta9/y)^2
paste0("the number of required replication for alternative2 is:", kamut_rizot_alternative2_b)


w <- (meanFlow6*0.074)
print(w)
kamut_rizot_alternative2_a <- 30*(delta6/w)^2
paste0("the number of required replication for alternative2 is:", kamut_rizot_alternative2_a)

```

as a result we chose 271 replication for alternative1 and 107 replication for alternative 2, and 32 for existing situation. We chose max replications for each alternative.
```{r}
filePathUtility_2 <- choose.files()
daily_utility_2 <- read.csv(filePathUtility_2,header=TRUE)
filePathProfit_2 <- choose.files()
daily_profit_2 <- read.csv(filePathProfit_2,header=TRUE)
```

```{r}
test10 <-  t.test(x= daily_profit_2$alternative1 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test10)
ci10 <-  c(test10$conf.int[1],test10$conf.int[2])
print(ci10)
meanFlow10 <- test10$estimate
delta10 <- test10$conf.int[2]-meanFlow10
print(delta10)
precise10 <-  abs(delta10/meanFlow10)
paste0("the relative accuracy for avarage daily profit for alternative1 is: ",  precise10)
```
עמד בדיוק היחסי
```{r}
test11 <-  t.test(x= daily_utility_2$existing.situation ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test11)
ci11 <-  c(test11$conf.int[1],test11$conf.int[2])
print(ci11)
meanFlow11 <- test11$estimate
delta11 <- test11$conf.int[2]-meanFlow11
print(delta11)
precise11 <-  abs(delta11/meanFlow11)
paste0("the relative accuracy for daily utility for existing situation is: ",  precise11)
```
לא עמד בדיוק היחסי
```{r}
test12 <-  t.test(x= daily_profit_2$alternative2 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test12)
ci12 <-  c(test12$conf.int[1],test12$conf.int[2])
print(ci12)
meanFlow12 <- test12$estimate
delta12 <- test12$conf.int[2]-meanFlow12
print(delta12)
precise12 <-  abs(delta12/meanFlow12)
paste0("the relative accuracy for avarage daily profit for alternative2 is: ",  precise12)
```
עמד בדיוק היחסי
```{r}
test13 <-  t.test(x= daily_utility_2$alternative2 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test13)
ci13 <-  c(test13$conf.int[1],test13$conf.int[2])
print(ci13)
meanFlow13 <- test13$estimate
delta13 <- test13$conf.int[2]-meanFlow13
print(delta13)
precise13 <-  abs(delta13/meanFlow13)
paste0("the relative accuracy for daily utility for alternative2 situation is: ",  precise13)
```
עמד בדיוק היחסי
```{r}
test14 <-  t.test(x= daily_utility_2$alternative1 ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test14)
ci14 <-  c(test14$conf.int[1],test14$conf.int[2])
print(ci14)
meanFlow14 <- test14$estimate
delta14 <- test14$conf.int[2]-meanFlow14
print(delta14)
precise14 <-  abs(delta14/meanFlow14)
paste0("the relative accuracy for daily utility for alternative1 situation is: ",  precise14)
```
עמד בדיוק היחסי

##כיוון שמדד נצילות עבר המצב הקיים לא עמד בדיוק היחסי נבצע איטרציה נוספת של חישוב מספר ריצות נדרש:
```{r}
z2 <- (meanFlow11*0.074)
print(z2)
kamut_rizot_alternative4 <- 32*(delta11/z2)^2
paste0("the number of required replication for existing situation is:", kamut_rizot_alternative4)

```
###נבדוק את הדיוק היחסי עבור חלופה זו ב34 ריצות :

```{r}
filePathUtility_3 <- choose.files()
daily_utility_3 <- read.csv(filePathUtility_3,header=TRUE)
```


```{r}
test15 <-  t.test(x= daily_utility_3$existing.situation ,y=NULL,alternative ="two.sided",conf.level=0.97)
print(test15)
ci15 <-  c(test15$conf.int[1],test15$conf.int[2])
print(ci15)
meanFlow15 <- test15$estimate
delta15 <- test15$conf.int[2]-meanFlow15
print(delta15)
precise15 <-  abs(delta15/meanFlow15)
paste0("the relative accuracy for daily utility for existing situation is: ",  precise15)
```
עמד בדיוק היחסי

#לסיכום, על מנת לעמוד בדיוק היחסי נבחר להריץ את המצב הקיים 34 ריצות, את חלופה 1 271 ריצות ואת חלופה 2 107 ריצות. 